Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-02-06 man/figures/plot_spei12.Rmd
update figures and chronos
add vertical lines

```{r plot_spei}
plot_spei <- spei %>%   
  ggplot(aes(x=date, y=spei, fill = sign)) + 
  geom_bar(stat = "identity", colour = "transparent") + 
  scale_fill_manual(values = c("pos" = "#696969", "neg" = "brown4")) +
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'gray') +
  labs(x = 'Year', y ='SPEI (12-month scale)') +
  scale_x_date(date_breaks = "5 year", date_labels = "%Y", 
               limits=as.Date(c("1949-01-01", "2015-12-01"))) +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none", 
        panel.grid = element_blank(), 
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(size=9),
        axis.title.y = element_text(size = 12))

>>>>

```{r plot_spei}
plot_spei <- spei %>%   
  ggplot(aes(x=date, y=spei, fill = sign)) + 
  geom_bar(stat = "identity", colour = "transparent") + 
  scale_fill_manual(values = c("pos" = "#696969", "neg" = "brown4")) +
  theme_bw() + 
  geom_hline(yintercept = 0, colour = 'gray') +
  labs(x = 'Year', y ='SPEI (12-month scale)') +
  scale_x_date(date_breaks = "5 year", date_labels = "%Y", 
               limits=as.Date(c("1949-01-01", "2015-12-01"))) +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none", 
        panel.grid = element_blank(), 
        axis.text.y = element_text(size=10),
        axis.text.x = element_text(size=9),
        axis.title.y = element_text(size = 12)) +
  geom_vline(xintercept = as.Date(c("2005-01-01", "2012-01-01")), colour = "grey", alpha = 0.8)
